---
title: "Getting Started with binomial"
author: "Siying Liu"
date: "2019.04.30"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial distribution

The package `"binomial"` is a implementation of functions for calculating probabilities of a Binomial random variable about the number of successes in a fixed number of random trials performed under identical conditions, and related calculations such as the probability distribution, cumulative distribution, and the expected value, variance, mode, skewness and kurtosis etc. 


### Number of combinations

`bin_choose()` takes two arguments: 
number of succeses k, number of trials n.

You can use function `bin_choose()` to get the number of combinations in which k successes can occur in n trials.

```{r}
num_combination <- bin_choose(n = 5, k = 2)
num_combination
```

### Probability

`bin_probability()` takes three arguments: 
number of succeses, number of trials, probability for each trial.

You can use function `bin_probability()` to get the probability of getting k successes in n trials.

`bin_probability()` will check whether all the arguments are valid, and will return an error message if there is any invalid input.

```{r}
prob <- bin_probability(success = 2, trials = 5, prob = 0.5)
prob
```

### Probability Distribution

`bin_distribution()` takes two arguments: 
number of trials, probability for each trial.

You can use function `bin_distribution()` to get the probability distribution of getting different number of successes in n trials.

The output will be a data.frame with two classes : c("bindis", "data.frame")

```{r}
prob_dis <- bin_distribution(trials = 5, prob = 0.5)
prob_dis
```

The `plot.bindis()` function gives you a barplot to display the probability histogram of a binomial distribution object "bindis"
```{r}
plot(prob_dis)
```


### Cumulative Probability Distribution

`bin_cumulative()` takes two arguments: 
number of trials, probability for each trial.

You can use function `bin_cumulative()` to get the cumulative distribution of getting different number of successes in n trials.

The output will be a data.frame with two classes : c("bincum", "data.frame")

```{r}
cum_dis <- bin_cumulative(trials = 5, prob = 0.5)
cum_dis
```

The `plot.bincum()` function gives you a plot of the cumulative distribution in an object "bincum"
```{r}
plot(cum_dis)
```


### Variables

`bin_variable()` takes two arguments: 
number of trials, probability for each trial.

You can use function `bin_variable()` to get the variables of a binomial distribution.

The output will be an object of class "binvar", a binomial random variable object.

`bin_variable()` will check whether all the arguments are valid, and will return an error message if there is any invalid input.

The `print.binvar()` function gives you a nice print of the content of an object "binvar"
```{r}
bin_var <- bin_variable(trials = 10, p = 0.3)
bin_var
```

The `summary.binvar()` function takes an object of class "binvar", returned output is a list of class "summary.binvar" containing named elements.

The `print.summary.binvar()` function nicely print the contents of an object "summary.binvar"
```{r}
binsum1 <- summary(bin_var)
binsum1
```


## Functions of measures
package also contain main functions for each of teh summary measures

### Mean
`bin_mean()` takes two arguments: 
number of trials, probability for each trial.

You can use function `bin_mean()` to get the expected value or mean for a binomial distribution, this is the expected number of successes in n trials.

```{r}
mean <- bin_mean(10, 0.3)
mean
```

### Variance
`bin_variance()` takes two arguments: 
number of trials, probability for each trial.

You can use function `bin_variance()` to get the variance for a binomial distribution.

```{r}
variance <- bin_variance(10, 0.3)
variance
```

### Mode
`bin_mode()` takes two arguments: 
number of trials, probability for each trial.

You can use function `bin_mode()` to get the mode for a binomial distribution, the most likely number of success in n dependent trials with probability p of sucess one each trial.

```{r}
mode <- bin_mode(10, 0.3)
mode
```

### Skewness
`bin_skewness()` takes two arguments: 
number of trials, probability for each trial.

You can use function `bin_skewness()` to get the skewness for a binomial distribution, a measure of asymmetry of the probability distribution fo a random variable about its mean

```{r}
skewness <- bin_skewness(10, 0.3)
skewness
```

### Kurtosis
`bin_kurtosis()` takes two arguments: 
number of trials, probability for each trial.

You can use function `bin_kurtosis()` to get the kurtosis for a binomial distribution, a measure of the "tailedness" of the probability distribution of a random variable.

```{r}
kurtosis <- bin_kurtosis(10, 0.3)
kurtosis
```

