---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

The package `"binomial"` is a [R](http://www.r-project.org/) package 
that provides function of a binomial distribution.

* `bin_choose()` generates the number of combinations in which k successes can occur in n trials in a binomial distribution.
* `bin_probability()` generates the probability of getting k successes in n trials in a binomial distribution.
* `bin_distribution()` generates the probability distribution of a binomial distribution.
* `bin_cumulative()` generates the cumulative distribution of a binomial distribution.
* `plot()` method for a `"bindis"` object to generate a barplot to display the probability histogram.
* `plot()` method for a `"bincum"` object to generate a scatter plot of the cumulative distribution.
* `summary()` method for a `"binvar"` object to generate a list of the summary output.

* `bin_mean()` generates the expected value or mean of a binomial distribution.
* `bin_variance()` generates the variance of a binomial distribution.
* `bin_mode()` generates the mode of a binomial distribution.
* `bin_skewness()` generates the skewness of a binomial distribution
* `bin_kurtosis()` generates the kurtosis of a binomial distribution.


## Motivation

This package has been developed to illustrate some of the concepts
behind the creation of an R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r}
# development version from GitHub:
# install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("siyingl6/binomial")
# install "binomial" (with vignettes)
devtools::install_github("siyingl6/binomial", build_vignettes = TRUE)
```

## Usage

```{r}
library(binomial)

# number of combination
num_combination <- bin_choose(n = 5, k = 2)
num_combination

# probability
prob <- bin_probability(success = 2, trials = 5, prob = 0.5)
prob

# probability distribution
prob_dis <- bin_distribution(trials = 5, prob = 0.5)
prob_dis
# barplot of probability distribution
plot(prob_dis)

# cumulative distribution
cum_dis <- bin_cumulative(trials = 5, prob = 0.5)
cum_dis
# scatter plot of cumulative distribution
plot(cum_dis)

# variables
bin_var <- bin_variable(trials = 10, p = 0.3)
bin_var
# summary measures of the binomial distribution
binsum1 <- summary(bin_var)
binsum1

# mean
mean <- bin_mean(10, 0.3)
mean

# variance
variance <- bin_variance(10, 0.3)
variance

# mode
mode <- bin_mode(10, 0.3)
mode

# skewness
skewness <- bin_skewness(10, 0.3)
skewness

# kurtosis
kurtosis <- bin_kurtosis(10, 0.3)
kurtosis
```
